% T I T L E   P A G E
% -------------------
% Last updated June 14, 2017, by Stephen Carr, IST-Client Services
% The title page is counted as page `i' but we need to suppress the
% page number. Also, we don't want any headers or footers.
\pagestyle{empty}
\pagenumbering{roman}

% The contents of the title page are specified in the "titlepage"
% environment.
\begin{titlepage}
        \begin{center}
        \vspace*{1.0cm}

        \Huge
        {\bf Neural-guidance for symbolic reasoning}

        \vspace*{1.0cm}

        \normalsize
        by \\

        \vspace*{1.0cm}

        \Large
        Nham Le \\

        \vspace*{3.0cm}

        \normalsize
        A thesis \\
        presented to the University of Waterloo \\ 
        in fulfillment of the \\
        thesis requirement for the degree of \\
        Master of Applied Science \\
        in \\
        Electrical and Computer Engineering \\

        \vspace*{2.0cm}

        Waterloo, Ontario, Canada, 2020 \\

        \vspace*{1.0cm}

        \copyright\ Nham Le 2020 \\
        \end{center}
\end{titlepage}

% The rest of the front pages should contain no headers and be numbered using Roman numerals starting with `ii'
\pagestyle{plain}
\setcounter{page}{2}

\cleardoublepage % Ends the current page and causes all figures and tables that have so far appeared in the input to be printed.
% In a two-sided printing style, it also makes the next page a right-hand (odd-numbered) page, producing a blank page if necessary.

 
% E X A M I N I N G   C O M M I T T E E (Required for Ph.D. theses only)
% Remove or comment out the lines below to remove this page
% \begin{center}\textbf{Examining Committee Membership}\end{center}
%   \noindent
% The following served on the Examining Committee for this thesis. The decision of the Examining Committee is by majority vote.
%   \bigskip
  
%   \noindent
% \begin{tabbing}
% Internal-External Member: \=  \kill % using longest text to define tab length
% External Examiner: \>  Bruce Bruce \\ 
% \> Professor, Dept. of Philosophy of Zoology, University of Wallamaloo \\
% \end{tabbing} 
%   \bigskip
  
%   \noindent
% \begin{tabbing}
% Internal-External Member: \=  \kill % using longest text to define tab length
% Supervisor(s): \> Doris Johnson \\
% \> Professor, Dept. of Zoology, University of Waterloo \\
% \> Andrea Anaconda \\
% \> Professor Emeritus, Dept. of Zoology, University of Waterloo \\
% \end{tabbing}
%   \bigskip
  
%   \noindent
%   \begin{tabbing}
% Internal-External Member: \=  \kill % using longest text to define tab length
% Internal Member: \> Pamela Python \\
% \> Professor, Dept. of Zoology, University of Waterloo \\
% \end{tabbing}
%   \bigskip
  
%   \noindent
% \begin{tabbing}
% Internal-External Member: \=  \kill % using longest text to define tab length
% Internal-External Member: \> Deepa Thotta \\
% \> Professor, Dept. of Philosophy, University of Waterloo \\
% \end{tabbing}
%   \bigskip
  
%   \noindent
% \begin{tabbing}
% Internal-External Member: \=  \kill % using longest text to define tab length
% Other Member(s): \> Leeping Fang \\
% \> Professor, Dept. of Fine Art, University of Waterloo \\
% \end{tabbing}

% \cleardoublepage

% D E C L A R A T I O N   P A G E
% -------------------------------
  % The following is a sample Delaration Page as provided by the GSO
  % December 13th, 2006.  It is designed for an electronic thesis.
  \noindent
This  thesis  consists  of  material  all  of  which  I  authored  or  co-authored: see  Statement of Contributions included in the thesis.  This is a true copy of the thesis,  including any required final revisions, as accepted by my examiners. 



  \bigskip
  
  \noindent
I understand that my thesis may be made electronically available to the public.

\cleardoublepage
\begin{center}
\textbf{Statement of Contributions}
\end{center}
Some of the text, figures and tables in this thesis are restated from our NeurIPS workshop paper \cite{Nham:nips19} and our current submission.

\textsc{Occam} was written by the researchers at The Computer Science Laboratory at SRI International.

Some of the source code for \textsc{Spacer} was written by Arie Gurfinkel.
\cleardoublepage
% A B S T R A C T
% ---------------

\begin{center}\textbf{Abstract}\end{center}
Symbolic reasoning was the founding father of Artificial Intelligence (AI). With the recent advances in Deep Learning, many traditional AI areas such as Computer Vision and Natural Language Processing have moved to probabilistic-based approaches. However, in applications where there is little to no room for uncertainty, such as Compiler or Software verification, symbolic reasoning is still the go-to option. In this thesis, we bring the advantage of data-driven learnable models into the precise world of symbolic reasoning. In particular, we choose to tackle two specific problems: Model Checking, in the context of Inductive Generalization, and Compiler Optimization, in the context of Software Debloating. We implemented our approach in two tools, named \textsc{Dopey} and \textsc{DeepOccam}, respectively. They both use traces generated from running a task to learn a better heuristic, and use said heuristic to improve subsequent runs of the same or similar tasks. Our results show that both neural-based heuristics outperform handcrafted heuristics.

\cleardoublepage

% A C K N O W L E D G E M E N T S
% -------------------------------

\begin{center}\textbf{Acknowledgements}\end{center}
I would like to thank Professor Arie Gurfinkel sharing their  expertise  in  the  subject,  availability  and  giving  valuable  advices  for  this  research. It goes without saying that this document would not be possible without him. 

I would like to thank Professor Werner Dietl and Professor Vijay Ganesh for attending the seminar, reviewing the thesis and providing valuable feedback on both occasions. 

I would like to thank the people at SRI International, especially Dr. Ashish Gehani and Dr. Jorge Navas, for the wonderful time I had there.

Finally, I would like to thank Dr. Xujie Sie for his deep insight into the world of neural-symbolic. This thesis would be nowhere near its current form without him.
% I would like to thank all the little people who made this thesis possible.
\cleardoublepage

% D E D I C A T I O N
% -------------------

\begin{center}\textbf{Dedication}\end{center}

This is dedicated to the one I love.
\cleardoublepage

% T A B L E   O F   C O N T E N T S
% ---------------------------------
\renewcommand\contentsname{Table of Contents}
\tableofcontents
\cleardoublepage
\phantomsection    % allows hyperref to link to the correct page

% L I S T   O F   T A B L E S
% ---------------------------
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% L I S T   O F   F I G U R E S
% -----------------------------
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% GLOSSARIES (Lists of definitions, abbreviations, symbols, etc. provided by the glossaries-extra package)
% -----------------------------
\printglossaries
\cleardoublepage
\phantomsection		% allows hyperref to link to the correct page

% Change page numbering back to Arabic numerals
\pagenumbering{arabic}

